Supplimentary Analysis

### 2021-11-17 Supplymentary.Rmd
*tab 1

hist(residual.6F, main = NULL, xlab = "Six factor Solution: Residuals",ylim=c(0, 400))
abline(h =65, lwd = 2, lty = 2)
abline(v =.05,lwd = 2, lty = 2)
sixFac <- tabledown::fac.tab(fa.6F.3, cut =.3,complexity = F)
```

@@

as_kable_extra(tz_table, format = "latex",booktabs = T) -> tz_kable

@@

tz_kable %>% kable_styling(latex_options = c("scale_down"))

>>>>

#hist(residual.6F, main = NULL, xlab = "Six factor Solution: Residuals",ylim=c(0, 400))
#abline(h =65, lwd = 2, lty = 2)
#abline(v =.05,lwd = 2, lty = 2)
sixFac <- tabledown::fac.tab(fa.6F.3, cut =.3,complexity = F)
```

@@

as_kable(tz_table, format = "latex",booktabs = T, longtable =T) -> tz_kable

@@

tz_kable %>% 
  kable_styling(latex_options = c("repeat_header")) %>% 
  column_spec(1,width = "10cm") %>% 
  column_spec(2,width = "2cm")
